### 2025-07-29 getting-started.qmd
20250724 - sort data
20250729 - fix

For instance, you can use the following code to load the `tidyverse` package [@R-tidyverse]:

```{r}
library("tidyverse")
```

@@

>>>>

For instance, you can use the following code to load the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) [@R-petersenlab] and `tidyverse` [@R-tidyverse] packages:

```{r}
library("petersenlab")
library("tidyverse")
```

@@

## Sort Data {#sec-sortData}

```{r}
players %>% 
  arrange(position, age) #sort by position (ascending) then by age (ascending)

players %>% 
  arrange(position, -age) #sort by position (ascending) then by age (descending)
```
